---
title: "DF Camera Trapping"
author: "Kelly Bruno"
date: "2023-01-31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Download and Load Packages
```{r packages}
# list.of.packages <- c("activity",
#                       "corrplot",
#                       "cowplot",
#                       "dplyr", 
#                       "elevatr",
#                       "gfcanalysis",  
#                       "ggplot2",
#                       "gridExtra",
#                       "iNEXT",
#                       "kableExtra",
#                       "Hmsc",
#                       "leaflet",
#                       "lme4",
#                       "lubridate",
#                       "magrittr",
#                       "MCMCvis",
#                       "MODISTools",
#                       "osmdata",
#                       "pals",
#                       "plotly",
#                       "remotes",
#                       "rmarkdown",
#                       "sf",
#                       "spOccupancy",
#                       "stars",
#                       "stringr",
#                       "terra",
#                       "tibble",
#                       "tidyr", 
#                       "unmarked",
#                       "viridis",
#                       "jtools",
#                       "vegan",
#                       "MuMIn",
#                       "rgdal",
#                       "usedist",
#                       "taxize")
# 
# # A check to see which ones you have and which are missing
# new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
# 
# # Code which tells R to install the missing packages
# if(length(new.packages)) install.packages(new.packages)
# lapply(list.of.packages, require, character.only = TRUE)
# 
# # We use the remotes package to access package repositories not on the 
# # CRAN interface (e.g. on github)
# library(remotes)
# 
# remotes::install_github("RS-eco/traitdata")
# remotes::install_github("arcaravaggi/remBoot")
# remotes::install_github("annam21/spaceNtime")
```

Backing up Data
Pictures will be saved in "placename" folders with nested "deployment_id" folders i.e. folder "-2845.621" with folders "-2845.621_1_1", "-2845.621_1_2"

Optional Preprocessing Steps

- Rename camera image with unique codes (placename_datetime)
- Use of AI labeler if you have many images to process (always check these)
- Timelapse extraction (if you for example take a photo every day at noon) using a package such as phenopix


#Metadata standardization
We need to keep accurate records of data collection

we are using the Wildlife Insights standards:
- Project data "proj.Rda" a dataframe containing key information about the project itself
- Image data "img.Rda" a dataframe containing all of the information contained within each image.
- Deployment data "dep.Rda" a dataframe listing the activity of the camera traps involved in your study, and any issues encountered during deployments
- Camera data "cam.Rda" a dataframe all the cameras deployed in the project


