---
title: "Covariates"
author: "Kelly Bruno"
date: "2023-04-05"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load data and packages}

rm(list = ls())

library(kableExtra);library(dplyr); library(sf); library(MODISTools); library(lubridate); library(corrplot); library(traitdata); library(terra); library(osmdata); library(elevatr)

# Start by reading in your species list
sp_summary <- read.csv("data/processed_data/Gate12_common_name_list.csv", header=T)
#rm last row (error)
sp_summary <- sp_summary[-34,-8]

#location level covs
locs <- read.csv("data/processed_data/Gate12_camera_locations.csv", header=T)

```

2 categories of covariate options
 a. Species traits
Traits are species-level covariates which we think are important in structuring their responses to other covariates, such as human modification
 b. Location-level covariates
 Location-level covariates are characteristics of the camera locations which are either fundamental to your question (such as the habitat type, degree of human modification, or distance to the nearest road), or they are things you are not directly interested in but must account for in your analyses.
 
```{r trait covariates}

#use package traitdata to add species traits
# This package isn't available on Cran, so we must use the remotes package
library(remotes)
#remotes::install_github("RS-eco/traitdata", build_vignettes = T, force=T)
# Load the library
library(traitdata)

#one of many datasets available
data("elton_mammals")

 head(elton_mammals) %>% kbl() %>% scroll_box(height = "200px") %>%
  kable_paper("striped", full_width = F)
 
#create column which matches species column in sp_summary dataset
elton_mammals$sp <- paste0(elton_mammals$Genus,"." ,elton_mammals$Species)

#subset to body mass value and activity data
tmp <- elton_mammals[, c("sp","BodyMass.Value", "Activity.Nocturnal", "Activity.Crepuscular",   "Activity.Diurnal")]

# Lets rename the columns to make them more usable
tmp <- tmp %>% rename(
              mass_g = BodyMass.Value,
              act_noct = Activity.Nocturnal,
              act_crep = Activity.Crepuscular,
              act_diur = Activity.Diurnal)

sp_summary <- left_join(sp_summary, tmp)

#check output
sp_summary %>% kbl() %>% scroll_box(height = "200px") %>%
  kable_paper("striped", full_width = F)

#rm weird genus issue
sp_summary <- sp_summary[-c(5,14,29,9,20,27,23,26,21,15,7,8,12,24,28),]

#ignore NAs as these are not identified to species level or are aves
write.csv(sp_summary, paste0("data/processed_data/", locs$project_id[1],"_species_list.csv"), row.names = F)

```
 
Link to traitdata datasets: https://opentraits.org/datasets.html

```{r camera station covs}
## load packages
library(leaflet)
library(htmlwidgets)
library(webshot)

#check locations
m <- leaflet() %>%             # call leaflet
        addProviderTiles(providers$Esri.WorldImagery) %>% # add imagery
        addCircleMarkers(      # Add circles for stations
          lng=locs$longitude, lat=locs$latitude, #these were wrong?
          popup=paste(locs$placename)) # include a popup with the placename!
m                      
saveWidget(m, "temp.html", selfcontained = FALSE)
webshot("temp.html", file = "studyarea_new.png",
        cliprect = "viewport")

#Lets convert our “normal” dataframe to an sf dataframe:
locs_sf <- st_as_sf(locs,                              # We specify the dataframe 
                    coords=c("longitude", "latitude"), # The XY coordinates
                    crs=4326)                          # And the projection code

locs_utm <- st_transform(locs_sf, crs=26712)

#plot points
plot(st_geometry(locs_utm))
axis(1)
axis(2)

#we could add local raster data here if we had it
#we can add elevation data
library(elevatr)
locs_sf <- get_elev_point(locs_sf, 
                          src="aws", #Amazon Web Service Terrain Tiles - available globally
                          z = 12)  # z specifies the zoom level, the lower the value the faster the code runs, but the coarser the elevation values are (units are in m)
boxplot(locs_sf$elevation) #small range as expected

#use Open Street Map (OSM) to generate other loc covariates
library(osmdata)

# First buffer our points to create an area of interest (aoi)
aoi <- st_bbox(st_buffer(locs_sf, 100)) # Units are in meters 

##Roads
#highway includes all roads and paths
highway <- opq(aoi) %>% #using the bounding box
           add_osm_feature(key="highway") %>% #extract all highway features
           osmdata_sf()  # convert them into simple features format

par(mfrow=c(1,3))
plot(st_geometry(highway$osm_points), main="osm_points")
plot(st_geometry(highway$osm_lines), main="osm_lines")
plot(st_geometry(highway$osm_polygons), main="osm_polygons")

par(mfrow=c(1,1))
plot(st_as_sfc(aoi))     # st_as_sfc created a polygon from a `bbox` object
plot(st_geometry(highway$osm_lines), add=T)
plot(st_geometry(locs_sf), col="red", add=T)

# Create an index of the nearest object in `highway$osm_lines` to locs_sf
index <- st_nearest_feature(locs_sf, highway$osm_lines)

# Use that index to ask for the distance to that object
locs_sf$road_dist_m <- st_distance(locs_sf, highway$osm_lines[index,], 
                                   by_element=T) # Note `by_element=T` tells st_distance to evaluate things line by line. 

##water bodies
#we know there is a pond at the site so this might not be useful

# First buffer our points to create an area of interest (aoi)
aoi <- st_bbox(st_buffer(locs_sf, 1000)) # Units are in meters

water <- opq(aoi) %>%
           add_osm_feature(key="water") %>%
           osmdata_sf()

par(mfrow=c(1,3))
plot(st_geometry(water$osm_points), main="osm_points")
# plot(st_geometry(water$osm_lines), main="osm_lines")
# plot(st_geometry(water$osm_polygons), main="osm_polygons")
index <- st_nearest_feature(locs_sf, water$osm_points)

locs_sf$water_dist_m <- st_distance(locs_sf, water$osm_points[index,], by_element=T) # Note `by_element=T` tells st_distance to evaluate things line by line.


#many more options for extraction, but not useful in such a small study area
```

OSM feature types: https://wiki.openstreetmap.org/wiki/Map_features

```{r convert covs}
# Convert columns to numeric
locs_sf$road_dist_m <- as.numeric(locs_sf$road_dist_m)

locs_sf$water_dist_m <- as.numeric(locs_sf$water_dist_m)

# Convert it back to a dataframe
locs_sf$geometry <- NULL

locs <- left_join(locs, locs_sf)


# Write the dataset

write.csv(locs, paste0("data/processed_data/", locs$project_id[1],"_camera_locations_and_covariates.csv"), row.names=F)
```


```{r correlations}

library(corrplot)

# First we need to create a correlation matrix between the different variables of interest
M <- cor(locs[, c("elevation",
                     "road_dist_m", "water_dist_m")])

corrplot(M,                              #The correlation matrix we made
         method="color",                 # How we want the cells 
         type="upper",                   # Just show the upper part (it is usually mirrored)
         order="hclust",                 # Order the variables using the hclust method
         addCoef.col = "black",          # Add coefficient of correlation  
         tl.col="black", tl.srt=45,      # Control the text label color and rotation
         diag=F                          # Suppress the diagonal correlations (which are 1 anyway)
         )

#if we are seeing pairwise correlations >0.7 we perhaps shouldn’t include those in the same model
#high correlation between road and water distance - lets take water out of the model
```
